---
title: "OMIS 482 - Fall 2024"
lang: en-US
output:
  examinr::exam_document:
    id: omis482_wcc1_t1
    version: 1
runtime: shiny_prerendered
---



```{r setup, include=FALSE}
# Set a CRAN mirror
options(repos = c(CRAN = "https://cloud.r-project.org"))

#Uncomment if the packages are not installed
#install.packages("googlesheets4")
#install.packages("dplyr") # for data manipulation
#install.packages("rsconnect")
library(examinr)
library(rsconnect)
library(googlesheets4)
library(base64enc)
library(rlang)
library(uuid)
library(dplyr)
library(shiny)

knitr::opts_chunk$set(echo = FALSE)


```


```{r,context='server-start'}

# Path to your service account JSON key file
json_path <- "dr-b-dashboard-project.json"

# Authenticate with Google Sheets using the service account key
gs4_auth(path = json_path)


# Google Sheets IDs
sheet_id <- "1se2CvGntBc5vWgJR-CrXGLYXR69NhGrE7vewmxScB1A"

# Function to read user data from Google Sheets
get_user_data <- function(sheet_id) {
  users <- read_sheet(sheet_id, sheet = "users")
  return(users)
}

# Get user data
users <- get_user_data(sheet_id)

# Set up token-based authentication

auth_provider <- ui_token_auth(
  users = users,
  token_label = "Enter your Token-ID",
  title = "Login",
  button_label = "Login",
  token_empty = "Login cannot be empty.",
  unauthorized = "The Token-ID is incorrect."
)

# Use the ZID field instead of user_id for identifying users
users$ZID <- users$ZID  # Ensure that the ZID field is used properly

# Function to serialize and base64 encode an R object
serialize_object <- function(object) {
  if (is.null(object)) return(NA_character_)
  raw_obj <- serialize(object, NULL)
  base64enc::base64encode(raw_obj)
}

# Function to base64 decode and unserialize a string back to an R object
deserialize_object <- function(base64_string) {
  if (is.null(base64_string) || !is.character(base64_string)) return(NULL)
  raw_obj <- base64enc::base64decode(base64_string)
  unserialize(raw_obj)
}



# Create a new attempt
create_attempt <- function(user, test_id, test_version_id, seed, started_at, ...) {
  attempt_id <- UUIDgenerate()
  user_obj_serialized <- serialize_object(user)
  row <- data.frame(
    attempt_id = attempt_id,
    user_id = user$user_id,
    test_id = test_id,
    test_version_id = test_version_id,
    user_obj = user_obj_serialized,
    seed = seed,
    started_at = format(started_at, "%Y-%m-%d %H:%M:%S"),
    finished_at = NA,
    points = NA
  )
  # Append the row to Google Sheets
  sheet_append(sheet_id, row, sheet = "attempts")
  return(attempt_id)
}


# Finish an attempt
finish_attempt <- function(attempt_id, finished_at, ...) {
  # Convert finished_at to POSIXct and format it
  finished_at_formatted <- format(as.POSIXct(finished_at), "%Y-%m-%d %H:%M:%S")
  
  # Read the current attempts from Google Sheets
  attempts <- read_sheet(sheet_id, sheet = "attempts")
  
  # Update the finished_at field for the specific attempt_id
  attempts <- attempts %>% 
    mutate(finished_at = ifelse(attempt_id == !!attempt_id, finished_at_formatted, finished_at))
  
  # Write the updated data back to Google Sheets
  sheet_write(attempts, sheet_id, sheet = "attempts")
  
  return(TRUE)
}


# Grade an attempt
grade_attempt <- function(attempt_id, points, ...) {
  attempts <- read_sheet(sheet_id, sheet = "attempts")
  
  # Ensure points are serialized and base64 encoded
  serialized_points <- tryCatch(
    serialize_object(points),
    error = function(e) {
      warning("Failed to serialize points: ", e$message)
      return(NA)
    }
  )
  
  if (is.na(serialized_points)) {
    return(FALSE) # Do not proceed if serialization fails
  }

  # Ensure the data size does not exceed the limit
  if (nchar(serialized_points) > 50000) {
    warning("Serialized points data exceeds the maximum size limit.")
    return(FALSE)
  }

  attempts <- attempts %>% 
    mutate(points = ifelse(attempt_id == !!attempt_id, serialized_points, points))

  sheet_write(attempts, sheet_id, sheet = "attempts")
  return(TRUE)
}

# Get attempts
get_attempts <- function(user, test_id, test_version_id, ...) {
  attempts <- read_sheet(sheet_id, sheet = "attempts")
  attempts$user_obj <- lapply(attempts$user_obj, function(x) {
    if (!is.na(x) && nchar(x) > 0) {
      deserialize_object(x)
    } else {
      NULL
    }
  })

  if (!is.null(user)) {
    attempts <- attempts[attempts$user_id == user$user_id, , drop = FALSE]
  }
  if (!is.null(test_id)) {
    attempts <- attempts[attempts$test_id == test_id, , drop = FALSE]
  }
  if (!is.null(test_version_id)) {
    attempts <- attempts[attempts$test_version_id == test_version_id, , drop = FALSE]
  }

  return(attempts)
}


# Save section data
save_section_data <- function(attempt_id, section, section_data, ...) {
  # Read existing section data
  existing_data <- read_sheet(sheet_id, sheet = "section_data")

  # Determine the next ID
  if (nrow(existing_data) == 0) {
    next_id <- 1
  } else {
    existing_ids <- as.numeric(existing_data$id)
    next_id <- max(existing_ids, na.rm = TRUE) + 1
  }

  # Create a new row with the next ID and other data
  row <- tibble(
    id = next_id,
    attempt_id = attempt_id,
    section = section,
    saved_at = as.character(Sys.time()),
    section_data = serialize_object(section_data)
  )

  # Append the new row to the Google Sheet
  sheet_append(sheet_id, data = row, sheet = "section_data")
  return(TRUE)
}



# Get section data
get_section_data <- function(attempt_id, section, ...) {
  section_data <- read_sheet(sheet_id, sheet = "section_data")
  section_data <- section_data %>% filter(attempt_id == !!attempt_id)
  
  if (!is.null(section)) {
    section_data <- section_data %>% filter(section == section)
  }
  section_data <- section_data %>%
    rowwise() %>%
    mutate(section_data = list(deserialize_object(section_data))) %>%
    ungroup()
  return(split(section_data, seq(nrow(section_data))))
}

# Get the last section for an attempt
get_last_section <- function(attempt_id, ...) {
  section_data <- read_sheet(sheet_id, sheet = "section_data")
  section_data <- section_data %>% filter(attempt_id == !!attempt_id)
  if (nrow(section_data) > 0) {
    last_section <- section_data$section[which.max(section_data$saved_at)]
    return(last_section)
  }
  return(NULL)
}

# Combine all functions into a storage provider list
google_sheets_storage_provider <- list(
  create_attempt = create_attempt,
  finish_attempt = finish_attempt,
  grade_attempt = grade_attempt,
  get_attempts = get_attempts,
  save_section_data = save_section_data,
  get_section_data = get_section_data,
  get_last_section = get_last_section
)

# Use this Google Sheets storage provider for the exam
exam_config(auth_provider = auth_provider, storage_provider = google_sheets_storage_provider)




```


# Weekly Coding Checkup 1

Welcome! We finally start working on the Dr. B & Class  project. During the entire semester you will apply what we learned in class in a set of tasks and scenarios custom designed for you. Please remember that it is important that the code that you submit is your own code and not somebody else work. It is fine to make mistakes but only by practicing in RStudio you can get a better grasp of the software. I also want you to try building your document as an official report for a potential company (Dreaming Diamonds LLC) for which you are getting to know and explore the diamonds dataset (e.g., spend time on storytelling, commenting results and providing insights and conclusions when possible).

<strong>TIP:</strong> Use diamonds dataset to answer the questions.

1.	Load the tidyverse package.
```{r q-1, exercise=TRUE, exercise.autocomplete=TRUE, exercise.solution="q-1-solution"}


```

```{r q-1-solution, echo =FALSE}
library(tidyverse)
```

2.	Assign the object diamonds (a dataset available as soon as tidyverse is loaded) to an object named “dreaming_diamonds”. 
[Hint: assign to dreaming_diamonds the object (dataset) diamonds]

```{r q-2, exercise=TRUE, exercise.autocomplete=TRUE, exercise.solution="q-2-solution"}


```

```{r q-2-solution, echo =FALSE}
dreaming_diamonds <- diamonds
```


3.	Use the mean function to compute the average of the “price” variable/column. Use the help function to learn more about the mean function. 
[Hint: use dreaming_diamonds$price inside the function). What is the average price of the diamonds in your dataset?]

```{r q-3, exercise=TRUE, exercise.autocomplete=TRUE, exercise.points=1, exercise.solution="q-3-solution"}


```

```{r q-3-solution, echo =FALSE}
average_price <- mean(dreaming_diamonds$price)
```

4.	Use the median function to compute the median of the “carat” variable/column. Use the help function to learn more about the median function.
[Hint: use dreaming_diamonds$carat inside the function). What is the median carat of the diamonds in your dataset?]

```{r q-4, exercise=TRUE, exercise.autocomplete=TRUE,exercise.points=1, exercise.solution="q-4-solution"}


```

```{r q-4-solution, echo = FALSE}
median_carat <- median(dreaming_diamonds$carat)
```

<div class="warning-box">
  <strong>Reminder:</strong> Make sure that you Run all the code chunks before clicking on Submit.
</div>



# Done!

You have successfully submitted the 1st Weekly Coding Checkup.

